Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-08-06 review/response.Rmd

The optimisation methods are further discussed in section 3.4 and depend on the structure present in the data. What is the value of these investigations for more realistic settings in which the structure is not known.

**It is important to understand the performance of the optimisation before applying the method on new examples and we use the known examples for this. This is now explained in the first sentence in Section 3.4.** XXX check

Finally, the relationship between the simulation study and the examples using the astrophysics data remains unclear. How are the physics applications linked to the simulation study and vice versa? Currently, the two aspects seem to me rather independent and could actually be presented in separate manuscripts. Moreover, since some rather important aspects of the simulation study have been put into an appendix. For the COST audience certainly the details of the simulation study are more relevant than the astrophysics application.

**As we now outline in the section overview, this paper first investigates the behaviour of the new indexes to understand the potential and challenges in using them in projection pursuit settings, before applying them to examples of the physics problems we are interested in addressing. While we agree that the simulation study is central to the work, we believe that showing applications of the method to unknown distributions is also relevant for the COST audience. Note that the application section now also contains guidelines on how to apply projection pursuit to new datasets, which are referenced in comments in the source code producing the examples, making them more useful to the reader** XXX check

### 2019-08-06 scagnostics.Rmd
why use physics data

This paper investigates the behaviour of these indexes. Section \ref{sec:construct} discusses index construction, and how they fit into the guided tour. Section \ref{sec:investigate} investigates the behaviour of the indexes, explored primarily using tour methods (@As85, @BCAH05, @CBCH94). The new guided tour with these indexes is applied to two examples from gravitational wave astronomy (Section \ref{sec:phys}).

>>>>

\textcolor{red}{This paper first investigates the behaviour of these indexes to understand the potential and challenges in using them in projection pursuit settings, before applying them to examples of the physics problems we are interested in addressing.}
Section \ref{sec:construct} discusses index construction, and how they fit into the guided tour. Section \ref{sec:investigate} investigates the behaviour of the indexes, explored primarily using tour methods (@As85, @BCAH05, @CBCH94). The new guided tour with these indexes is applied to two examples from gravitational wave astronomy (Section \ref{sec:phys}).
